Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-05-16 prop_letter.tex
Updates from ShareLaTeX

We will proceed by assuming a crypto-deterministic QIVMP $\bar{\mu}$
and derive a contradiction using the following nine ``Mermin square''
observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{equation}
\begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
\sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
\sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
\end{aligned}
\label{eq:MerminSquare}
\end{equation}

>>>>

We will proceed by assuming a crypto-deterministic QIVMP $\bar{\mu}$
and derive a contradiction using the following nine ``Mermin-Peres square''
observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{center}
\begin{tabular}{| c | c | c |}
\hline
$\mathbb{1} \otimes\sigma_{z}$ & $\sigma_{z}  \otimes\mathbb{1}$ & $\sigma_{z} \otimes\sigma_{z}$  \\ \hline
$\sigma_{x} \otimes\mathbb{1}$ & $\mathbb{1} \otimes\sigma_{x}$ & $\sigma_{x} \otimes\sigma_{x}$ \\ \hline
$\sigma_{x} \otimes\sigma_{z}$ & $\sigma_{z} \otimes\sigma_{x}$ & $\sigma_{y} \otimes\sigma_{y}$ \\ \hline
\end{tabular}
\label{eq:MerminSquare}
\end{center}
